More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-06-12 2016-Weak-FH-Bisim/WeakBisim.tex
weak bisi

@@

>>>>

\RAB{We let $\gamma$ range over sets of words and use $\dotcup$ as the union that appends sets of words.}

@@

\RAB{Weak bisimularity can be checked by reducing it to strong bisimularity. For this, we need to added in Definition \ref{def:buildweakOT} the following rule: }

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\tau} s''} \in \WT
}
 \end{mathpar}
\RAB{Given an open automaton  $A$, we can built a weak open automaton, denoted $A^{\omega}$, from rules given in Definition \ref{def:buildweakOT}. So weak bisimularity on $A$ coincides with strong bisimularity on $A^{\omega}$, than we can prove weak bisimularity with strong bisimularity on $A^{\omega}$.}
